LAGOS lake depth

### 2020-01-15 figures/01_contrasts.Rmd
print intermediate figs

gg_depth_reservoir <- dt %>%
  dplyr::filter(!is.na(reservoir_class)) %>%
  group_by(reservoir_class) %>%
  summarize(lake_maxdepth_m = list(tibble::enframe(
    quantile(lake_maxdepth_m, probs = c(0.05,0.5,0.95), na.rm = TRUE)))) %>% 
  unnest() %>%
  tidyr::spread(name, value) %>%
  ggplot() +
geom_pointrange(aes(x = reservoir_class, y = `50%`, 
                      ymin = `5%`, ymax = `95%`)) +
  ylab("Depth (m)") + xlab("")
```

@@

gg_depth_xtabs <- group_by(dt_sub, 
                           lake_glaciatedlatewisc, reservoir_class) %>%
    summarize(lake_maxdepth_m = list(tibble::enframe(
    quantile(lake_maxdepth_m, probs = c(0.05,0.5,0.95), na.rm = TRUE)))) %>% 
  unnest() %>%
  tidyr::spread(name, value) %>%
  tidyr::unite(cat, lake_glaciatedlatewisc:reservoir_class) %>%
  ggplot() +
geom_pointrange(aes(x = cat, y = `50%`, 
                      ymin = `5%`, ymax = `95%`)) +
  ylab("Depth (m)") + xlab("")

>>>>

(gg_depth_reservoir <- dt %>%
  dplyr::filter(!is.na(reservoir_class)) %>%
  group_by(reservoir_class) %>%
  summarize(lake_maxdepth_m = list(tibble::enframe(
    quantile(lake_maxdepth_m, probs = c(0.05,0.5,0.95), na.rm = TRUE)))) %>% 
  unnest() %>%
  tidyr::spread(name, value) %>%
  ggplot() +
geom_pointrange(aes(x = reservoir_class, y = `50%`, 
                      ymin = `5%`, ymax = `95%`)) +
  ylab("Depth (m)") + xlab(""))
```

@@

(gg_depth_xtabs <- group_by(dt_sub, 
                           lake_glaciatedlatewisc, reservoir_class) %>%
    summarize(lake_maxdepth_m = list(tibble::enframe(
    quantile(lake_maxdepth_m, probs = c(0.05,0.5,0.95), na.rm = TRUE)))) %>% 
  unnest() %>%
  tidyr::spread(name, value) %>%
  tidyr::unite(cat, lake_glaciatedlatewisc:reservoir_class) %>%
  ggplot() +
geom_pointrange(aes(x = cat, y = `50%`, 
                      ymin = `5%`, ymax = `95%`)) +
  ylab("Depth (m)") + xlab(""))
